---
title: "utah-univ-roi"
author: "Jeff Olson"
date: "4/16/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Considering a bachelor’s degree in Utah? Learn its economic value from government sources. 

###### Click a button for the identity of the university.
```{r, echo = FALSE, cache = TRUE}
warning = FALSE
library(leaflet)
library(tidyr)
univ_sites <- data.frame(
        name = c("Utah State University",
                 "Weber State University",
                 "University of Utah",
                 "Utah Valley University",
                 "Brigham Young University",
                 "Snow College",
                 "Southern Utah University",
                 "Dixie State University"
        ),
        lat = c(41.7452675,
                41.1914258,
                40.7649408,
                40.278766,
                40.2518476,
                39.3612287,
                37.6764503,
                37.1032184
        ),
        lng = c(-111.8138713,
                -111.9465433,
                -111.8442908,
                -111.7175626,
                -111.6515043,
                -111.5851162,
                -113.0734888,
                -113.5674376
        ),
        col = c("blue",
                "purple",
                "red",
                "green",
                "blue",
                "orange",
                "red",
                "red")
)

univ_sites %>%
        leaflet() %>%
        addTiles() %>%
        addCircleMarkers(lng = univ_sites$lng,
                         lat = univ_sites$lat,
                         color = univ_sites$col, 
                         popup = univ_sites$name
        )

```

## Here is what you will learn:

--Median debt to the federal government  
--Median earnings two years after graduation  
--Economic return (calculated from debt and earnings) 

## 

### Not a complete story, but valuable. 
### For privacy, the government does not provide information about small programs.

## Try it at 

https://jefferyeolson.shinyapps.io/utah-univ-roi/  
